---
title: "April 4th Check-In"
author: "Evelyn Cai"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load libraries

library(tidyverse)
library(ggplot2) # 2.2.1
library(cregg)
library(cjoint) # 2.0.6
library(foreign)
library(readstata13)
library(skimr)
library(rstanarm)
library(sjPlot)

# Read in data
hoc <- read.dta13("HoC_merged.dta")
```

First we have to pre-process the data. In the following section, I define the following new variables:

* `chooseprofile` on whether the randomized hypothetical candidate was chosen
* `incumbencyxtasky` where x is either 1 or 2 and y is 1 through 10 for a total of 20 differently defined variables
* `genderxtasky` where same thing as above^
* `agextasky` ^
* `educationxtasky` ^
* `hometownxtasky` ^
* `occupationxtasky`
* `politicsxtasky` ^

Then we will pivot longer the following columns:
incumbency1task incumbency2task gender1task gender2task age1task age2task education1task education2task occupation1task occupation2task politics1task politics2task hometown1task hometown2task

Make the following series of renames:
rename incumbency1task c_incumbency1
rename incumbency2task c_incumbency2
rename gender1task c_gender1
rename gender2task c_gender2
rename age1task c_age1
rename age2task c_age2
rename education1task c_education1 
rename education2task c_education2
rename occupation1task c_occupation1
rename occupation2task c_occupation2
rename politics1task c_politics1
rename politics2task c_politics2
rename hometown1task c_hometown1
rename hometown2task c_hometown2

*rename incumbency1 c_incumbency1
*rename incumbency2 c_incumbency2
*rename gender1 c_gender1
*rename gender2 c_gender2
*rename age1 c_age1
*rename age2 c_age2
*rename education1 c_education1 
*rename education2 c_education2
*rename occupation1 c_occupation1
*rename occupation2 c_occupation2
*rename politics1 c_politics1
*rename politics2 c_politics2
*rename hometown1 c_hometown1
*rename hometown2 c_hometown2

Pivot longer the following:
reshape long c_incumbency c_gender c_age c_education c_occupation c_politics c_hometown

Create the following variables:
c_local = "都道府県以内"
c_politics2 = c_politics
c_incumbencyid = 0
label_incumbency = "Newcomer"
c_genderid = 0
label_gender = "Male"
c_ageid = 0
label_age = "42"
c_localid = 0
label_local = "Outside prefecture"
c_educationid = 0
label_education = "High school"
c_occupationid = 0
label_occupation = "Company employee"
c_politicsid = 0
label_politics = "No background"
agebias = 0



Make the following recodes:
replace chooseprofile = 1 if Conjoint_A1_num == 1 & profile == 1 & task == 1
replace chooseprofile = 1 if Conjoint_A1_num == 2 & profile == 2 & task == 1
replace chooseprofile = 1 if Conjoint_A2_num == 1 & profile == 1 & task == 2
replace chooseprofile = 1 if Conjoint_A2_num == 2 & profile == 2 & task == 2
replace chooseprofile = 1 if Conjoint_A3_num == 1 & profile == 1 & task == 3
replace chooseprofile = 1 if Conjoint_A3_num == 2 & profile == 2 & task == 3
replace chooseprofile = 1 if Conjoint_A4_num == 1 & profile == 1 & task == 4
replace chooseprofile = 1 if Conjoint_A4_num == 2 & profile == 2 & task == 4
replace chooseprofile = 1 if Conjoint_A5_num == 1 & profile == 1 & task == 5
replace chooseprofile = 1 if Conjoint_A5_num == 2 & profile == 2 & task == 5
replace chooseprofile = 1 if Conjoint_A6_num == 1 & profile == 1 & task == 6
replace chooseprofile = 1 if Conjoint_A6_num == 2 & profile == 2 & task == 6
replace chooseprofile = 1 if Conjoint_A7_num == 1 & profile == 1 & task == 7
replace chooseprofile = 1 if Conjoint_A7_num == 2 & profile == 2 & task == 7
replace chooseprofile = 1 if Conjoint_A8_num == 1 & profile == 1 & task == 8
replace chooseprofile = 1 if Conjoint_A8_num == 2 & profile == 2 & task == 8
replace chooseprofile = 1 if Conjoint_A9_num == 1 & profile == 1 & task == 9
replace chooseprofile = 1 if Conjoint_A9_num == 2 & profile == 2 & task == 9
replace chooseprofile = 1 if Conjoint_A10_num == 1 & profile == 1 & task == 10
replace chooseprofile = 1 if Conjoint_A10_num == 2 & profile == 2 & task == 10

replace c_local = "都道府県以外" if c_hometown == "北海道以外"
replace c_local = "都道府県以外" if c_hometown == "青森県以外"
replace c_local = "都道府県以外" if c_hometown == "岩手県以外"
replace c_local = "都道府県以外" if c_hometown == "宮城県以外"
replace c_local = "都道府県以外" if c_hometown == "秋田県以外"
replace c_local = "都道府県以外" if c_hometown == "山形県以外"
replace c_local = "都道府県以外" if c_hometown == "福島県以外"
replace c_local = "都道府県以外" if c_hometown == "栃木県以外"
replace c_local = "都道府県以外" if c_hometown == "茨城県以外"
replace c_local = "都道府県以外" if c_hometown == "群馬県以外"
replace c_local = "都道府県以外" if c_hometown == "埼玉県以外"
replace c_local = "都道府県以外" if c_hometown == "千葉県以外"
replace c_local = "都道府県以外" if c_hometown == "東京都以外"
replace c_local = "都道府県以外" if c_hometown == "三重県以外"
replace c_local = "都道府県以外" if c_hometown == "京都府以外"
replace c_local = "都道府県以外" if c_hometown == "佐賀県以外"
replace c_local = "都道府県以外" if c_hometown == "兵庫県以外"
replace c_local = "都道府県以外" if c_hometown == "和歌山県以外"
replace c_local = "都道府県以外" if c_hometown == "大分県以外"
replace c_local = "都道府県以外" if c_hometown == "大阪府以外"
replace c_local = "都道府県以外" if c_hometown == "奈良県以外"
replace c_local = "都道府県以外" if c_hometown == "宮崎県以外"
replace c_local = "都道府県以外" if c_hometown == "富山県以外"
replace c_local = "都道府県以外" if c_hometown == "山口県以外"
replace c_local = "都道府県以外" if c_hometown == "山梨県以外"
replace c_local = "都道府県以外" if c_hometown == "岐阜県以外"
replace c_local = "都道府県以外" if c_hometown == "岡山県以外"
replace c_local = "都道府県以外" if c_hometown == "島根県以外"
replace c_local = "都道府県以外" if c_hometown == "広島県以外"
replace c_local = "都道府県以外" if c_hometown == "徳島県以外"
replace c_local = "都道府県以外" if c_hometown == "愛媛県以外"
replace c_local = "都道府県以外" if c_hometown == "愛知県以外"
replace c_local = "都道府県以外" if c_hometown == "新潟県以外"
replace c_local = "都道府県以外" if c_hometown == "沖縄県以外"
replace c_local = "都道府県以外" if c_hometown == "滋賀県以外"
replace c_local = "都道府県以外" if c_hometown == "熊本県以外"
replace c_local = "都道府県以外" if c_hometown == "石川県以外"
replace c_local = "都道府県以外" if c_hometown == "神奈川県以外"
replace c_local = "都道府県以外" if c_hometown == "福井県以外"
replace c_local = "都道府県以外" if c_hometown == "福岡県以外"
replace c_local = "都道府県以外" if c_hometown == "長崎県以外"
replace c_local = "都道府県以外" if c_hometown == "長野県以外"
replace c_local = "都道府県以外" if c_hometown == "静岡県以外"
replace c_local = "都道府県以外" if c_hometown == "香川県以外"
replace c_local = "都道府県以外" if c_hometown == "高知県以外"
replace c_local = "都道府県以外" if c_hometown == "鳥取県以外"
replace c_local = "都道府県以外" if c_hometown == "鹿児島県以外"

replace c_politics2 = "都道府県議会議員" if c_politics == "北海道議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "青森県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "岩手県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "宮城県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "秋田県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "山形県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "福島県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "栃木県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "茨城県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "群馬県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "埼玉県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "千葉県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "東京都議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "三重県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "京都府議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "佐賀県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "兵庫県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "和歌山県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "大分県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "大阪府議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "奈良県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "宮崎県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "富山県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "山口県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "山梨県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "岐阜県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "岡山県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "島根県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "広島県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "徳島県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "愛媛県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "愛知県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "新潟県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "沖縄県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "滋賀県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "熊本県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "石川県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "神奈川県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "福井県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "福岡県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "長崎県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "長野県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "静岡県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "香川県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "高知県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "鳥取県議会議員"
replace c_politics2 = "都道府県議会議員" if c_politics == "鹿児島県議会議員"

replace c_incumbencyid = 1 if c_incumbency == "元職 (1回)"
replace c_incumbencyid = 2 if c_incumbency == "元職 (2回以上)"
replace c_incumbencyid = 3 if c_incumbency == "現職 (1回)"
replace c_incumbencyid = 4 if c_incumbency == "現職 (2回以上)"

replace label_incumbency = "Former, 1 term" if c_incumbencyid == 1
replace label_incumbency = "Former, 2+ terms" if c_incumbencyid == 2
replace label_incumbency = "Current, 1 term" if c_incumbencyid == 3
replace label_incumbency = "Current, 2+ terms" if c_incumbencyid == 4
labmask c_incumbencyid, values(label_incumbency)

replace c_genderid = 1 if c_gender == "女性"

replace label_gender = "Female" if c_genderid == 1
labmask c_genderid, values(label_gender)

replace c_ageid = 1 if c_age == "47歳"
replace c_ageid = 2 if c_age == "55歳"
replace c_ageid = 3 if c_age == "69歳"
replace c_ageid = 4 if c_age == "70歳"

replace label_age = "47" if c_ageid == 1
replace label_age = "55" if c_ageid == 2
replace label_age = "69" if c_ageid == 3
replace label_age = "70" if c_ageid == 4
labmask c_ageid, values(label_age)

replace c_localid = 1 if c_local == "都道府県以内"

replace label_local = "Inside prefecture" if c_localid == 1
labmask c_localid, values(label_local)

replace c_educationid = 1 if c_education == "地方国立大卒"
replace c_educationid = 2 if c_education == "東大卒"
replace c_educationid = 3 if c_education == "大学院卒"

replace label_education = "Regional university" if c_educationid == 1
replace label_education = "University of Tokyo" if c_educationid == 2
replace label_education = "Graduate school" if c_educationid == 3
labmask c_educationid, values(label_education)

replace c_occupationid = 1 if c_occupation == "国家公務員"
replace c_occupationid = 2 if c_occupation == "新聞記者"
replace c_occupationid = 3 if c_occupation == "自衛官"
replace c_occupationid = 4 if c_occupation == "タレント"

replace label_occupation = "National bureaucrat" if c_occupationid == 1
replace label_occupation = "Newspaper reporter" if c_occupationid == 2
replace label_occupation = "Self-Defense Forces" if c_occupationid == 3
replace label_occupation = "Celebrity/talent" if c_occupationid == 4
labmask c_occupationid, values(label_occupation)

replace c_politicsid = 1 if c_politics2 == "都道府県議会議員"
replace c_politicsid = 2 if c_politics2 == "議員秘書"
replace c_politicsid = 3 if c_politics2 == "世襲政治家"

replace label_politics = "Prefectural assembly" if c_politicsid == 1
replace label_politics = "MP secretary" if c_politicsid == 2
replace label_politics = "Dynastic politician" if c_politicsid == 3
labmask c_politicsid, values(label_politics)

replace agebias = 1 if age_leaders == "Don't know"
replace agebias = 2 if age_leaders == "Agree"
replace agebias = 2 if age_leaders == "Strongly agree"

Lastly, use the cregg package to create cj plots for each treatment group, with the outcome variable as chooseprofile and by~treatment_group


```{r amce_plots}

# Select only for the relevant variables
# hoc_1 <- cj(hoc, formula = Y.1 ~ Party + Age + Experience + Hometown + Education + Previous_Occupation, estimate = "amce", by = ~Gender)
# 
# DD_diff <- cj(DD, formula = Y.1 ~ Party + Age + Experience + Hometown + Education + Previous_Occupation, estimate = "amce_diff", by = ~Gender)

```

